Reproducible and programmatic generation of neuroimaging visualisations

### 2022-03-18 manuscript.Rmd
sp check

This article will cover three major advantages of using code-generated
visualisations over GUI based tools: replicability, flexibility and
integration. First, by generating figures using code, you increase the
replicability of your figures for yourself, your collaborators and your
readers. Second, code-based software provide more precise controls over
visualisation settings, while also benefiting from advantages of
programming, such as being able to iteratively generate multiple
figures. Finally, being able to integrate figure generation into your
analysis scripts reduces changes of errors, with more advanced tools now
allowing for seamless weaving together of prose and code. Here, we
review the advantages of learning and using programmatic neuroimaging
visualisations, focusing on benefits to replicability, flexibility and
interactivity. We conclude by introducing examples of R-packages which
allow for visualisation of region-of-interest (ROI), voxel, vertex and
edge level data, followed by a brief discussion of limitations and
functionality gaps in code-based brain visualisation tools.

>>>>

This article will cover three major advantages of using code-generated
visualisations over GUI based tools: replicability, flexibility and
integration. First, by generating figures using code, you increase the
replicability of your figures for yourself, your collaborators and your
readers. Second, code-based software provide more precise controls over
visualisation settings, while also benefiting from advantages of
programming, such as being able to iteratively generate multiple
figures. Finally, being able to integrate figure generation into your
analysis scripts reduces chances of errors, with more advanced tools now
allowing for seamless weaving together of prose and code. Here, we
review the advantages of learning and using programmatic neuroimaging
visualisations, focusing on benefits to replicability, flexibility and
interactivity. We conclude by introducing examples of R-packages which
allow for visualisation of region-of-interest (ROI), voxel, vertex and
edge level data, followed by a brief discussion of limitations and
functionality gaps in code-based brain visualisation tools.
